### 2024-07-18 evaluating-prediction-accuracy.qmd
20240718 - more info on miscalibration

The various types of miscalibration are depicted in @fig-miscalibration:

@@

>>>>

The various types of general miscalibration are depicted in @fig-miscalibration:

@@

However, predictions could also be miscalibrated in more specific ways.
For instance, predictions could be well-calibrated at all predicted probabilities except for a given predicted probability (e.g., 20%).
Or, the predictions could be miscalibrated but not systematically over- or underpredicted.
Thus, it is important to evaluate a calibration plot to evaluate the extent to which the predictions are miscalibrated and the pattern of that miscalibration.
